---
title: "Simulation and model analysis"
subtitle: "Non Linear Dynamics"
author: "Frederik Espersen Knudsen"
date: as.character(Sys.Date())
output: pdf_document
---

# LAC Operon Model analysis
Based on Yildirim et al. 2004.

See repository for more information.

## Setup
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(broom)
```

\newpage
# Scan of appropriate time step size
### Loading simulation results
Loading and structuring data:
```{r echo=FALSE}
timestep_results_dir = "../Results/Timestep scan/2022-11-15 16:32:05"

timestep_data <-
  tibble(Filename = list.files(timestep_results_dir, pattern=".csv")) %>%
  mutate(Data = map(paste(timestep_results_dir, Filename, sep="/"), read.csv)) %>%
  unnest(Data) %>%
  pivot_longer(c(M, B, A), names_to="Species", values_to="Concentration") %>%
  select(-Filename) %>%
  nest(Data = c(Time, Species, Concentration))

timestep_data %>% glimpse()
timestep_data %>% pluck("Data", 1) %>% head()
```

###  Visualizing results
```{r echo=FALSE}
timestep_data %>%
  unnest(Data) %>%
  filter(Concentration > 0 & Concentration < 1000000000) %>%
  mutate(Timestep = Timestep * 60 * 1e3) %>%
  ggplot(aes(x=Time, y=Concentration, color=Model, lty=Model)) +
    geom_line(alpha=0.5) +
    geom_point(size=0.2) +
    facet_grid(Species~Timestep, scales="free_y") +
    labs(title="Time course of species by time step size [ms]",
         subtitle="Scan of time step size") +
    xlab("Time [s]") +
    ylab("Concentration [nM]") +
    theme_bw()

timestep_data %>%
  unnest(Data) %>%
  filter(Concentration > 0 & Concentration < 1000000000) %>%
  mutate(Timestep = Timestep * 60 * 1e3,
         Time = Time * 60) %>%
  filter(Time < 1.8) %>%
  ggplot(aes(x=Time, y=Concentration, color=Model, lty=Model)) +
    geom_line(alpha=0.5) +
    geom_point(size=0.2) +
    facet_grid(Species~Timestep, scales="free_y") +
    labs(title="Time course of species by time step size [ms]",
         subtitle="Scan of time step size") +
    xlab("Time [s]") +
    ylab("Concentration [nM]") +
    theme_bw()
```





\newpage
# Scan of starting conditions

### Loading simulation results
Loading and structuring data:
```{r echo=FALSE}
conditions_results_dir = "../Results/Starting conditions scan/2022-11-15 16:33:20"

conditions_data <-
  tibble(Filename = list.files(conditions_results_dir, pattern=".csv")) %>%
  mutate(Data = map(paste(conditions_results_dir, Filename, sep="/"), read.csv)) %>%
  unnest(Data) %>%
  pivot_longer(c(M, B, A), names_to="Species", values_to="Concentration") %>%
  select(-Filename) %>%
  nest(Data = c(Time, Species, Concentration))

conditions_data %>% glimpse()
conditions_data %>% pluck("Data", 1) %>% head()
```

### Visualizing results
```{r}
conditions_data %>%
  unnest(Data) %>%
  mutate(Time = Time * 60,
         L = L * 1e-3) %>%
  filter(Time < 3) %>%
  ggplot(aes(x=Time, y=Concentration, color=Model, fill=paste0(M_0, B_0, A_0))) +
    geom_line(size=0.1) +
    scale_y_log10() +
    facet_grid(Species~L, scales="free_y") +
    labs(title="Time course of species by lactose concentrations [µM]",
         subtitle="Scan of starting conditions") +
    xlab("Time [s]") +
    ylab("Concentration [nM]") +
    theme_bw()
```

### Analysing model differences
Checking null hypothesis: There is no difference between the original and corrected model.
```{r}
conditions_data %>%
  unnest(Data) %>%
  nest(Data=c(Time, Concentration)) %>%
  slice(1)
```
